---
title: "top10s"
output: html_document
editor_options: 
  chunk_output_type: console
---

# This document sets up our table that involves the top Billboard songs from the years 2010-2019 and the corresponding spotify data. In this chunk we loaded in various packages to clean the data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(stringr)
library(rvest)
library(httr)
library(spotifyr)
library(dplyr)
library(plotly)
library(googlesheets4)
```


```{r}
# read in the data set from our project folder
top10s <- read_csv("music_data/top10s.csv")
top10s
```


## Cleaning Up the Genre Category
```{r}
# renamed the genre categories and combined the least frequent ones into an "other" category to find the most frequent genre within the popular songs

top10s <-top10s %>%
  separate((`top genre`), c("variable","genre"), extra='merge')

other <-c("complextro","downtempo","brostep","electro","electronic","escape","folk-pop","hollywood","house","irish","permanent","neo","metropolis","tropical")
top10s$genre[top10s$variable %in% other]  <- 'Other'
top10s$genre[top10s$variable =='hip']  <- 'hip hop'
top10s$genre[top10s$variable =='latin']  <- 'latin'
top10s$genre[top10s$variable =='boy']  <- 'pop'
top10s$genre[top10s$variable =='french']  <- 'pop'
top10s$genre[top10s$variable =='electropop']  <- 'pop'
top10s$genre[top10s$variable =='pop']  <- 'pop'
top10s$genre[top10s$genre=='contemporary r&b'] <-'r&b'
top10s$genre[top10s$genre=='room'] <-'Other'
top10s(top10s$genre)

miss <- colSums(is.na(top10s))
print(miss[miss>0])

top10s <-na.omit(top10s)

table(top10s$genre)
```


## Scraping Data for Billie Eilish on Spotify
```{r}
Sys.setenv(SPOTIFY_CLIENT_ID = '7146273e81e047be9f0bf7465f96a768')
Sys.setenv(SPOTIFY_CLIENT_SECRET = '22a02478c98346dba8783d6f1d474808')

# Personal tokens provided by Spotify.
access_token <- get_spotify_access_token()
access_token

# Getting Spotify's audio information for Billie Eilish (danceability, energy, etc.).
billie <- get_artist_audio_features("billie eilish")

# Removing colums that we will not be analyzing. 
billie_tidy <- billie[-c(1:6, 8, 11, 13, 16, 20:25, 27:29, 31, 33:35, 37:39)]

# Filtering out albums that we will not be using and rearranging the columns to match the Spotify 2010-2019 dataset.
billie_eilish <- billie_tidy %>%
  as_tibble() %>%
  filter(album_name != "Happier Than Ever") %>%
  distinct() %>%
  select(track_number, track_name, tempo, energy, danceability, loudness, liveness, valence, duration_ms, acousticness, speechiness, album_name, album_release_year)

# Changing the variables' values to be consistent with the 2010-2019 dataset.
billie_eilish <- billie_eilish %>%
  mutate(danceability = danceability * 100) %>%
  mutate(energy = energy * 100) %>%
  mutate(speechiness = speechiness * 100) %>%
  mutate(acousticness = acousticness * 100) %>%
  mutate(liveness = liveness * 100) %>%
  mutate(valence = valence * 100) %>%
  mutate(duration_ms = duration_ms / 1000) %>%
    rename(duration = duration_ms)

write_csv(billie_eilish, "music_data/billie_eilish.csv")
```

# Scraping Billie Eilish lyrics from Google Sheet
```{r}
# the Spotify read lyrics function was not working, so we put the lyrics in a Google sheet and read into a csv file called "eilish_lyrics"
eilish_lyrics <- read_csv("music_data/eilish_lyrics.csv")
```

# Finding the Correlations for Spotify Data ("Compare Two Variables")
```{r}
top10s_correlation <- top10s[-c(1:5)]

top10s_correlation2 <- round(cor(top10s_correlation),
  digits = 2)

top10s_correlation2
```

# Finding the Correlations for 2019 Spotify Data ("Compare Variables of Top 2019 Songs")
```{r}
top10s_correlation_19 <- top10s[-c(1:4)] %>% filter(year == "2019")

top10s_2019_corr <- round(cor(top10s_correlation_19),
  digits = 2)

top10s_2019_corr
```

# Finding the Correlations for Billie Eilish ("Compare Variables of Top 2019 Songs")
```{r}
billie_correlation <- billie_eilish[-c(1:2, 12:13)]

billie_correlation2 <- round(cor(billie_correlation),
  digits = 2)

billie_correlation2
```